Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-04-24 sections/4gluing_alt.tex
..

\begin{proof}[Proof of \Cref{thm:gluing_lcfas}]
    In the case that all $\infty$-categoies involved are locally constant we will extend the previous proof to provide the equivalence. Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property. Let $U \xhookrightarrow{} V$ be two disks of $M$. What we have to check is that there is an equivalence
    %
    \begin{equation}
        \int_U \gamma(A_-, A_+) \xrightarrow{\ \ \simeq \ \ } \int_V \gamma(A_-, A_+)
    \end{equation}
    %
    in $\catC$. We will achieve this if we find compatible equivalences,
    %
    \begin{align}
        &\int_{U_-} A_- \simeq \int_{V_-} A_-& &\int_{U_0 \times \mathbb{R}} A_0 \simeq \int_{V_0 \times \mathbb{R}} A_0& &\int_{U_+} A_+ \simeq \int_{V_+} A_+,&
    \end{align}
    %
    on each of the pieces $(U_- \xhookrightarrow{} V_-), (U_0 \times \mathbb{R} \xhookrightarrow{} V_0 \times \mathbb{R}), (U_+ \xhookrightarrow{} V_+)$, and combine them using the bar construction. If these pieces were disks then the above equivalences would be given by the local constancy of the constituent locally constant factorization algebras.

@@

%\begin{conjecture}
%    The theory of factorization algebras is fully determined, using factorization homology, by the data of a functor
%    %
%    \begin{equation}
%        \mathsf{Bsc} \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
%    \end{equation}
%    %
%    In the locally constant case, we can even say that to each basic $U$ this functor attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
%\end{conjecture}
%
%\begin{remark}
%    The $\infty$-category of basics $\mathsf{B}_{U}$ for our purposes provides a kind of generalization of framing, which makes calculation easier.
%\end{remark}

>>>>

\begin{proof}[Proof of \Cref{thm:gluing_lcfas}]
    In the case that all $\infty$-categories involved are locally constant we will extend the previous proof to provide the equivalence. Since we know that restriction does not destroy local constancy, extending the result to the case of locally constant factorization algebras simply requires us to show that the gluing $\gamma$ also preserves this property. Let $U \xhookrightarrow{} V$ be two disks of $M$. What we have to check is that there is an equivalence
    %
    \begin{equation}
        \int_U \gamma(A_-, A_+) \xrightarrow{\ \ \simeq \ \ } \int_V \gamma(A_-, A_+)
    \end{equation}
    %
    in $\catC$. We will achieve this if we find compatible equivalences,
    %
    \begin{align}
        &\int_{U_-} A_- \simeq \int_{V_-} A_-& &\int_{U_0 \times \mathbb{R}} A_0 \simeq \int_{V_0 \times \mathbb{R}} A_0& &\int_{U_+} A_+ \simeq \int_{V_+} A_+,&
    \end{align}
    %
    on each of the pieces $(U_- \xhookrightarrow{} V_-), (U_0 \times \mathbb{R} \xhookrightarrow{} V_0 \times \mathbb{R}), (U_+ \xhookrightarrow{} V_+)$, and combine them using the bar construction. If these pieces were disks then the above equivalences would be given by the local constancy of the constituent locally constant factorization algebras.

@@
